tl20-05_berghei_pir_DESEQ

### 2021-10-01 chapter3_results_bergheiPir/Manuscript_berghei_pir_DESEQ.Rmd
Use cool grep technique to append '\n' to column names

```{r heatmap}
#Add a new-line to the S6 label so that it doesn't overlap with others
pir_column_split <- gsub(pir_clade$clade[match(colnames(sig_pirs_cast), pir_clade$Geneid)],
                         pattern = 'ancestral',
                         replacement = 'a')
pir_column_split <- ifelse(pir_column_split %in% c('S6', 'L2'), 
                           paste0(pir_column_split, '\n'),
                           pir_column_split)

>>>>

```{r heatmap}
#Add a new-line to the S6 label so that it doesn't overlap with others
pir_column_split <- gsub(
  gsub(pir_clade$clade[match(colnames(sig_pirs_cast), pir_clade$Geneid)],
       pattern = 'ancestral',
       replacement = 'a'),
  pattern = '(S6|L2)',
  replacement = '\\1\n'
)
